Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-06 paper/main.tex
minor wording tweaks and TODO notes

To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos automatically isolates packages installed via \texttt{smuggle} statements using a custom scheme called ``projects.'' Functionally, a Davos project is similar to a standard Python virtual environment (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}): it consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular project or task. However, Davos projects do not need to be manually activated and deactivated, do not contain separate Python or \texttt{pip} executables, and \textit{extend} the user's main Python environment rather than replace it.

@@

\item \texttt{.project}: This attribute is a string that specifies the name of
the ``project'' associated with the current notebook. As described in
Section~\ref{subsec:projects}, a notebook's project determines where and how
any \texttt{smuggle}d dependencies are installed if they are not available in
the current runtime environment. By default, this attribute is named according
to the current notebook's absolute file path. However, the project name may be
customized to enable shared dependency installations across notebooks (see
Sec.~\ref{subsec:projects}).

>>>>

To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos automatically isolates packages installed via \texttt{smuggle} statements using a custom scheme called ``projects.'' Functionally, a Davos project is similar to a standard Python virtual environment (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}): it consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular project or task. However, unlike standard virtual environments, Davos projects do not need to be manually activated and deactivated, do not contain separate Python or \texttt{pip} executables, and \textit{extend} the user's main Python environment rather than replace it.

@@

\item \texttt{.project}: \textcolor{red}{\textbf{TODO: fix this}} This attribute is a string that specifies the name of
the ``project'' associated with the current notebook. As described in
Section~\ref{subsec:projects}, a notebook's project determines where and how
any \texttt{smuggle}d dependencies are installed if they are not available in
the current runtime environment. By default, this attribute is named according
to the current notebook's absolute file path. However, the project name may be
customized to enable shared dependency installations across notebooks (see
Sec.~\ref{subsec:projects}).
